%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Math 3250 Combinatorics, University of Connecticut
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Anything after a percent sign is a comment.

% Necessary first line. \documentclass defines the type of document and some options (for example, try changing the font size (10pt or 11pt or 12pt).
\documentclass[12pt]{amsart}
\usepackage{enumerate} % to be able to enumerate a list using non-numbers
\usepackage{tikz}
%for hypertext references
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = red,
            anchorcolor = green]{hyperref}


\usepackage[letterpaper]{geometry} % from 2016
\geometry{tmargin=0.63in,bmargin=-0.0in,lmargin=1.50in,rmargin=1.50in}
\voffset -0.5in

% The part of the tex file between the \documentclass and \begin{document} line is called the preamble.  Things having to do with setting up the document are done in the preamble.  You will not need to mess with it for now, except to change your name and the title of your document. 
% After adding your name next to author, head down to where it says "Start here"

\title{Math3250 Combinatorics Reading HW 5}
%\author{your preferred first and last name:}
%\date{due d1, Week 4}
\begin{document}

\maketitle

% --------------------------------------------------------
%                         Start here
% --------------------------------------------------------

%\noindent Credit: 
%Write down everyone who helped you, including classmates who contributed to your thought process. Write down Bona's textbook and other written sources you used as well.

\subsection*{Instruction}
Please submit all sections. Both handwritten or typed solutions are accepted.


Read the first two pages of Sec 3.3 Choice Problems in B\'ona's ``A Walk Through Combinatorics" textbook, pg 50--51. Start with the ``lottery drawings in Hungary".

\bigskip


\section{Binomial coefficient definition}
Copy Def 3.15 for the \emph{binomial coefficients} $\binom{n}{k}$.



\section{Binomial coefficient formula}
Copy Theorem 3.16 and write down the proof in the book. Add extra sentences to make the proof more clear.


\section{Complement}
\begin{enumerate}[i.]
\item 
Write down Def 3.17.
\item 
Let $S:= \{1,2,5 \} \subset [5]$ and write down $S^c$, the complement of $S^c$.

\item 
What is the complement of $[n]$, as a subset of itself?

\item 
What is the complement of $\emptyset$, as a subset of $[n]$?

\end{enumerate}







\section{An identity for the binomial coefficients}
Write the statements and proofs for Prop 3.18(1) and (2).


\section{Optional}
Read at least the problems given in Example 3.19 and 3.20 (on page 52), so that your brain can start thinking about them.


\section{Survey}
\begin{enumerate}[i.] 
\item Approximately how much time did you spend on this homework?
%\item Write down the resources (for example, B\'ona's textbook or a  \href{https://math.stackexchange.com/}{math.stackexchange.com/} page) you referenced and the people that you talked with.	
\item Any questions about this homework?
\end{enumerate}



\end{document}
